`respR` - An R package for the analysis of respirometry data

### 2017-11-13 manuscript/LaTeX/manuscript.Rmd
manuscript updates

keywords: "R, software, respirometry, metabolic rate"
thanks: "Replication files are available on the first author's Github account (http://github.com/januarharianto). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: januar.harianto@sydney.edu.au."

@@

In intermittent flow respirometry, $O_2$ concentration is measured as described above, but periodically the chamber is flushed with new water or air, returning it to initial conditions, resealed, and the experiment repeated (Svendsen et al., 2016). This technique is essentially closed respirometry, but with the incorporation of repeated measures. Depending on the metabolic rate metric being investigated, final respiration rate can be calculated as the mean of the measures [e.g. @carey_sea_2016], or the lowest or highest rates recorded in any trial [e.g. @stoffels_physiological_2015].

@@

```{r Figure3, echo = F, fig.cap="Typical graphical outputs of the function `auto.rate()`. **(A)** Depending on the `method` input, the function is able to show: (clockwise form top left) the maximum rate detected, the minimum rate detected, calculation of rate by fixed-width intervals, and the most linear region as determined by kernel density estimates. **(B)** In addition, the outputs will also print diagnostic plots of: (clockwise from top left) the rolling regression of rate as a function of time with dotted lines indicating the region used to estimate the parameter, a kernel density plot that shows only when the `linear` method is called, a residual plot of the regression, and a normal Q-Q plot of the residuals of the regression. Analysis is performed using the example dataset `sardine`, which is included in the package. Code to reproduce the plots is available in the Supplementary Material."}

>>>>

keywords: "R, software, respirometry, metabolic rate"
thanks: "Replication files are available on the first author's Github account (http://github.com/januarharianto). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: nicholas.carey@sams.ac.uk."

@@

In intermittent flow respirometry, $O_2$ concentration is measured as described above, but periodically the chamber is flushed with new water or air, returning it to initial conditions, resealed, and the experiment repeated [@svendsen_design_2016]. This technique is essentially closed respirometry, but with the incorporation of repeated measures. Depending on the metabolic rate metric being investigated, final respiration rate can be calculated as the mean of the measures [e.g. @carey_sea_2016], or the lowest or highest rates recorded in any trial [e.g. @stoffels_physiological_2015].

@@

```{r Figure3, echo = F, fig.cap="Typical graphical outputs of the function `auto.rate()`. **(A)** Depending on the `method` input, the function is able to show: (clockwise form top left) the maximum rate detected, the minimum rate detected, calculation of rate by fixed-width intervals, and the most linear region as determined by kernel density estimates. **(B)** In addition, the outputs will also print diagnostic plots of: (clockwise from top left) the rolling regression of rate as a function of time with dotted lines indicating the region used to estimate the parameter, a kernel density plot that shows only when the `linear` method is called, a residual plot of the regression, and a normal Q-Q plot of the residuals of the regression. Analysis is performed using the example dataset `sardine.rd`, which is included in the package. Code to reproduce the plots is available in the Supplementary Material."}
